The Astropy Project

### 2017-12-19 main.tex

\author{Astropy Collaboration}

@@

The \package{astropy.table} subpackage provides functionality for
representing and manipulating heterogeneous data. In some respects,
this is similar to \package{numpy} record arrays \citep{numpy} or
\package{pandas} dataframes \citep{pandas} but with modifications for
astronomical data. Most notably, tables from \package{astropy.table}
allow for table or column metadata and can handle
vectors or arrays as table entries.
The package was described in
detail in \cite{astropy}.  Thus, in what follows, we only summarize
key new features or updates to \package{astropy.table} since the
previous \astropy paper. These are support for grouped table
operations, table concatnation, and using array-valued
\package{astropy} objects as table columns.

>>>>

\author{Astropy Project}
\noaffiliation
\footnote{The author list has three parts: the 13 authors that made significant contributions to the  writing of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.  The position in the author list does not correspond to contributions to the \astropy Project as a whole.  A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}

\input{author.tex}

@@

The \package{astropy.table} subpackage provides functionality for
representing and manipulating heterogeneous data. In some respects,
this is similar to \package{numpy} record arrays \citep{numpy} or
\package{pandas} dataframes \citep{pandas} but with modifications for
astronomical data. Most notably, tables from \package{astropy.table}
allow for table or column metadata and can handle
vectors or arrays as table entries.
The subpackage was described in
detail in \cite{astropy}.  Thus, in what follows, we only summarize
key new features or updates to \package{astropy.table} since the
previous \astropy paper. These are support for grouped table
operations, table concatnation, and using array-valued
\package{astropy} objects as table columns.
